\documentclass{article}

\usepackage[margin=0.5in]{geometry}
\setlength\parindent{0pt}
\title{3D Printer Rules and Guidelines}
\author{Neve Laughery}

\begin{document}

\maketitle

\section{Administration}

The 3D printing administrator will be chosen each semester by the Edinboro Computer Science executive board. They will be responsible for the following:

\begin{itemize}
	\item Maintaining the 3D printer
	\begin{itemize}
		\item Calibrating the machine when needed
		\item Ordering filament
		\item Researching and solving technical issues related to the machine
	\end{itemize}
	\item Discussing viability of projects with users
	\item Managing each user's print quota
	\item Creating time slots to avoid scheduling conflicts
\end{itemize}

\subsection{Contingencies}

In the case that the printer is broken beyond repair the Edinboro Computer Science Club executive board must vote to determine what to do with what remains of the printer.

In the case that the club ceases to exist the department chair will decide what to do with the 3D printer.

\subsection{Location}

The printer should be kept in the Computer Science Research Room, Ross 129.

Excess filament should be kept in the Server room, Ross 124.

\section{Users}

Failure to follow these rules and guidelines will result in an indefinite ban which can only be lifted by a club vote

\subsection{Eligibility}

Users should be members of the Edinboro University Computer Science Club. Members of this club will be given priority scheduling over non-members. Prints requested by non-member Edinboro University students will be approved or declined at the discretion of the administrator. In both cases the user must discuss their project with the administrator before printing.

\subsection{Print Quota}

Users will be allotted TBA prints per academic year, this will be tracked by the administrator. If a user wishes to exceed this quota they must first get express permission by the administrator.

\subsection{Filament Used}

Users will weigh their projects, including failed prints, on the scale located next to the printer. Users will pay 10\% more than the cost of filament per gram of filament used to the Edinboro Computer Science Club Treasurer. This amount is slightly more than the cost of the filament to account for wear and tear on the machine.

If a user wants to use their own filament for a print it should be discussed with the administrator first.

The Creality Ender 3 can print the following filaments in 1.75 mm:

\begin{itemize}
	\item PLA
	\item TPU
	\item ABS
\end{itemize}

\subsection{Failed Prints}

Users are responsible for their own failed prints. Should a print fail the user can either consult the Troubleshooting document or request help from the
administrator. Users must pay for all filament used including failed prints.

\end{document}
